### 2014-01-21 abstract.tex
Kathy's corrections

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid in PCa
diagnosis and management by evaluating the structural composition of prostate
zones and tumors based on their stiffness.  In this study, MR and ARFI imaging
datasets were compared to one another and with gross pathology measurements
made immediately post radical prostatectomy.  Images were manually segmented to
delineate the central gland (CG) and prostate capsule, and 3D models were
rendered to evaluate zonal anatomy dimensions and volumes.  Both imaging
modalities showed moderate correlations between estimated organ volume and
gross pathologic weights.  ARFI and MR total prostate gland volumes were
well-correlated (R$^2$ = \MRarfiVolTotalRsq), but ARFI images yielded prostate
volumes that were, on average, larger (\MRarfiVolTotalMeanDiff\% $\pm$
\MRarfiVolTotalStdDiff\%) than MR images, primarily due to over-estimation of
the lateral dimension of the total gland (\ARFImrTotalLatLatMeanPct $\pm$
\ARFImrTotalLatLatStdPct\%), while over-estimates of the other dimensions were
less significant (\ARFImrTotalAntPostMeanPct $\pm$ \ARFImrTotalAntPostStdPct\%
and \ARFImrTotalApexBaseMeanPct $\pm$ \ARFImrTotalApexBaseStdPct\%).  The ARFI
and MR CG volumes were also well-correlated (R$^2$ = \MRarfiVolCentralRsq).  CG
volume differences were attributed to under-estimation of the apex-to-base axis
(\ARFImrCentralApexBaseMeanPct $\pm$ \ARFImrCentralApexBaseStdPct\%), and
over-estimation bias in the lateral dimension (\ARFImrCentralLatLatMeanPct
$\pm$ \ARFImrCentralLatLatStdPct\%).  ARFI prostate imaging yielded prostate
volumes and dimensions that were correlated with MR T2WI estimates, with biases
in the AP dimension, most likely related to poor displacement SNR in the
anterior region of the prostate from greater distance from the rectal wall
imaging surface.  Lateral dimension contrast was also challenging due to
peri-prostatic fat.  ARFI imaging is a promising low-cost, real-time imaging
modality that can compliment MR imaging for diagnosis, treatment planning and
management of PCa.

>>>>

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer-related death.
Multi-parametric Magnetic Resonance Imaging (mpMRI) has gained recent
popularity to characterize PCa.  ARFI imaging has the potential to aid in PCa
diagnosis and management by evaluating the structural composition of prostate
zones and tumors based on their stiffness.  In this study, \invivo MR and ARFI
imaging datasets were compared to one another and with gross pathology
measurements made immediately post radical prostatectomy.  Images were manually
segmented in 3D Slicer to delineate the central gland (CG) and prostate
capsule, and 3D models were rendered in 3D Slicer to evaluate zonal anatomy
dimensions and volumes.  Both imaging modalities showed moderate correlations
between estimated organ volume and gross pathologic weights.  ARFI and MR total
prostate gland volumes were well-correlated (R$^2$ = \MRarfiVolTotalRsq), but
ARFI images yielded prostate volumes that were, on average, larger
(\MRarfiVolTotalMeanDiff\% $\pm$ \MRarfiVolTotalStdDiff\%) than MR images,
primarily due to over-estimation of the lateral dimension of the total gland
(\ARFImrTotalLatLatMeanPct $\pm$ \ARFImrTotalLatLatStdPct\%), while differences
in the other dimensions were less significant (\ARFImrTotalAntPostMeanPct $\pm$
\ARFImrTotalAntPostStdPct\%, anterior-to-posterior, and
\ARFImrTotalApexBaseMeanPct $\pm$ \ARFImrTotalApexBaseStdPct\%, apex-to-base).
The ARFI and MR CG volumes were also well-correlated (R$^2$ =
\MRarfiVolCentralRsq).  CG volume differences were attributed to
under-estimation of the apex-to-base axis (\ARFImrCentralApexBaseMeanPct $\pm$
\ARFImrCentralApexBaseStdPct\%), and over-estimation bias in the lateral
dimension (\ARFImrCentralLatLatMeanPct $\pm$ \ARFImrCentralLatLatStdPct\%).
ARFI prostate imaging yielded prostate volumes and dimensions that were
correlated with MR T2WI estimates, with biases in the AP dimension, most likely
related to poor displacement SNR in the anterior region of the prostate due to
greater distance from the rectal wall imaging surface.  Lateral dimension
contrast was also challenging due to peri-prostatic fat.  ARFI imaging is a
promising low-cost, real-time imaging modality that can compliment mpMRI for
diagnosis, treatment planning and management of PCa.
